---
title: "p8105_hw1_fp2513"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Loading penguins dataset

Here's a **code chunk** to load the _penguins_ data set:

```{r}
data("penguins", package = "palmerpenguins")

```

# Section 2

The next section writes a short description of the penguins data set:
The variable data set has `colnames(penguins, do.NULL = TRUE, prefix = "col")`
as column names, `nrow(penguins)` rows, `ncol(penguins)` columns, and the mean
flipper length is `mean(penguins$flipper_length_mm, na.rm=TRUE)`

```{r}
penguins_df = 
  colnames(penguins, do.NULL = TRUE, prefix = "col")
  colnames(penguins)

  nrow(penguins) 
  ncol(penguins) 
  
  mean(penguins$flipper_length_mm, na.rm=TRUE)
```

# Section 3

Making a scatter plot of the flipper length (mm) (y-axis) against bill length 
(mm) (x-axis); color indicates different species

```{r yx_scatter}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = bill_length_mm, y = flipper_length_mm, 
                           color = species)) +
ggtitle("Bill and Flipper length of Penguin species")
ggsave("20240916 Penguins scatter plot.pdf")
```
