---
title: "p8105_hw1_fp2513"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(dbplyr)
```

## Loading penguins dataset

Here's a **code chunk** to load the _penguins_ data set:

```{r}
data("penguins", package = "palmerpenguins")

```

## Describing the Penguins dataset

The next section writes a short description of the penguins data set. This includes respectively, the column names, the number of rows, the number of columns, and the mean flipper length in mm (and the code to retrieve those results)

```{r}
penguins_df = 

  print(colnames(penguins))
  
  nrow(penguins) 
  ncol(penguins) 
  
  mean(penguins %>% 
         pull(flipper_length_mm), na.rm = TRUE)
```

The columns in the penguins data set include: species, island, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex, and year. There are 344 rows and 8 columns. The mean flipper length of these penguins in mm is 200.9152


# Section 3

Making a scatter plot of the flipper length (mm) (y-axis) against bill length 
(mm) (x-axis); color indicates different species

```{r yx_scatter}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = bill_length_mm, y = flipper_length_mm, 
                           color = species), na.rm = TRUE) +
ggtitle("Bill and Flipper length of Penguin species")
```

```{r, eval = FALSE}
ggsave("20240916 Penguins scatter plot.pdf")
```


## HW1 Problem 2

Creating a data frame comprised of:
1. A random sample of size 10 from a standard Normal distribution
2. A logical vector indicating whether elements of the sample are greater than 0
3. A character vector of length 10
4. A factor vector of length 10, with 3 different factor “levels”

```{r df_create}
set.seed(1234)

numeric_col <- rnorm(10, sd = 1)
logical_col <- as.logical(numeric_col > 0)
character_col <- sample(c(letters), 10, replace = FALSE)
factor_col <- as.factor(sample(c("Level1", "Level2", "Level3"), 10, replace = TRUE))

df <- data.frame(
  Numeric_Column = numeric_col,
  Logical_Column = logical_col,
  Character_Column = character_col,
  Factor_Column = factor_col
)

print(df)
```

Take the mean of each variable in your dataframe.
(Numeric and Logical work, but Character and Factor do not)
```{r}
mean(df %>% pull(Numeric_Column))

mean(df %>% pull(Logical_Column))

mean(df %>% pull(Character_Column))

mean(df %>% pull(Factor_Column))
```

Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output)

```{r, eval = FALSE}
as.numeric(df %>% pull(Logical_Column))
as.numeric(df %>% pull(Character_Column))
as.numeric(df %>% pull(Factor_Column))

```

What happens, and why? Does this help explain what happens when you try to take the mean?


Converting the logical column into a numeric turns the TRUE FALSE into binary 1 and 0 respectively

Converting the character values into numeric, but since characters are not numeric, the output is NA for each character value

Converting the factor values maps each level of the factor into an integer code (here 3 levels so either 1, 2 or 3)

