---
title: "p8105_hw1_fp2513"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(dbplyr)
```

## Loading penguins dataset

Here's a **code chunk** to load the _penguins_ data set:

```{r}
data("penguins", package = "palmerpenguins")

```

## Describing the Penguins dataset

The next section writes a short description of the penguins data set. This includes respectively, the column names, the number of rows, the number of columns, and the mean flipper length in mm (and the code to retrieve those results)

```{r}
penguins_df = 
    colnames(penguins, do.NULL = TRUE, prefix = "col")
  colnames(penguins)
  
  nrow(penguins) 
  ncol(penguins) 
  
mean(penguins %>% pull(flipper_length_mm), na.rm = TRUE)

```

# Section 3

Making a scatter plot of the flipper length (mm) (y-axis) against bill length 
(mm) (x-axis); color indicates different species

```{r yx_scatter}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = bill_length_mm, y = flipper_length_mm, 
                           color = species)) +
ggtitle("Bill and Flipper length of Penguin species")
ggsave("20240916 Penguins scatter plot.pdf")
```
